\section{Background}{}\mbox \
\label{sec:background}

The main idea behind CAPTCHAs is to provide users with a task which only a human can perform, and cannot yet be performed by automated web programs, known as 'bots'. Two-factor authentication is a relatively new mechanism to make sure that the email and phone number of the user is confirmed to authenticate them as real users, although it requires extra effort on the users' part. Text based challenges are still very lucrative and are widely used control mechanisms to prevent automated form filling as they do not require any extra effort in the form of learning, training or access to mobile phones.\newline

Text based challenges evolved over time from being simple fonts embedded in images to cursive, handwritten text. With the evolution of Computer Vision over time, simple challenges proved ineffective in beating bots and the systems were redesigned to use a combination of distorted handwritten text with a lot of noise in the form of background images, skewed lines and using both black and white text. Speech based challenges came soon after their visual counterparts \cite{kochanski2002reverse, chan2003using} and just like advancements in Computer Vision, there have been similar advancements in natural language processing and in speech-to-text conversion. According to Shirali-Shahreza et al.\cite{shirali2011accessibility} three groups of people have trouble with this form of CAPTCHA - Visually impaired, who constitute 2.6\% of the world's population, users with dyslexia, and users suffering from motor impairment diseases like Parkinson's.\newline

Google introduced reCAPTCHA v2.0 in the year 2014, with the tagline 'Easy on humans, tough on bots'. The new version claimed to use an "advanced risk analysis sytem" that eased users' efforts in solving CAPTCHA challenges. As opposed to the garbled text with random digits and words, this version required the user to click in a checkbox or solve challenges with images. This improved the user experience, while solving the same purpose as the text challenges and was seen as a welcome change by users.\newline

